### 2018-07-15 arxiv/paper.tex
First round of fixes for v2 of arxiv paper

Our method derives from the radiative transfer equation (RTE), which expresses the change of the radiance field $L$, with respect to an infinitesimal change of position in direction $\omega$ at point $\vec{x}$:
\begin{align}
%\label{eq:rte}
\left(\nabla\cdot\omega\right)L\left(\vec{x}, \omega \right)
=&
-\sigma_t\left(\vec{x}\right) L\left(\vec{x}, \omega \right)\nonumber\\
&
+\sigma_s\left(\vec{x}\right) \int_{\Omega}
{
p\left(\omega'\cdot\omega\right)L\left(\vec{x}, \omega' \right)\ud\omega'
}\nonumber\\
&
+Q\left(\vec{x}, \omega\right)\nonumber
\  .
\label{eq:rte}
\end{align}

@@

So far, we have only given the $P_N$-equations in high-level operator notation (Equation~\ref{eq:pn_operator_notation}). Carrying out the full derivation creates large, unwieldy equations and requires a string of expansions and applications of identities. These are challenging to manipulate if done by hand. We \rev{therefore used a computer algebra representation}, which allowed us to derive and discretize the $P_N$-equation in a semi-automatic fashion (Figure~\ref{fig:car})).

@@

Since the real-valued SH bases (Equation~\ref{eq:sh_real_basis}) have different definitions for $m<0$, $m=0$ or $m>0$,  we get different projections for $\mathcal{S}^{l,m}$, depending on the sign of $m$.
%\vspace{5in}
%\begin{align}
%&-\frac{1}{2}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m+1}{4pt}}
%%\\
%+\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m+1}{4pt}}
%%\\
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m-1}{4pt}}
%%\\
%+\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}e^{{l-1,m+1}}
%\partial_x
%L^{\scaleto{l-1,m+1}{4pt}}
%%\\
%+\frac{1}{2}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m+1}{4pt}}
%%\\
%-\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m-1}{4pt}}
%\nonumber
%\\&
%+a^{\scaleto{l-1,m}{4pt}}
%\partial_z
%L^{\scaleto{l-1,m}{4pt}}
%%\\
%+b^{\scaleto{l+1,m}{4pt}}
%\partial_z
%L^{\scaleto{l+1,m}{4pt}}
%%\\
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%%\\
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%%\\
%= Q^{\scaleto{l,m}{4pt}}
%\label{eq:rpn_m_<_z}
%\end{align}

For $m=0$ we have
\begin{align}
&
\frac{1}{\sqrt{2}}c^{\scaleto{l-1,-1}{4pt}}\partial_x L^{\scaleto{l-1,1}{4pt}}
-\frac{1}{\sqrt{2}}d^{\scaleto{l+1,-1}{4pt}}\partial_x L^{\scaleto{l+1,1}{4pt}}
%\\&
\frac{1}{\sqrt{2}}c^{\scaleto{l-1,-1}{4pt}}\partial_y L^{\scaleto{l-1,-1}{4pt}}
\nonumber
\\&
-\frac{1}{\sqrt{2}}d^{\scaleto{l+1,-1}{4pt}}\partial_y L^{\scaleto{l+1,-1}{4pt}}
%\\&
+a^{\scaleto{l-1,0}{4pt}}\partial_z L^{\scaleto{l-1,0}{4pt}}
+b^{\scaleto{l+1,0}{4pt}}\partial_z L^{\scaleto{l+1,0}{4pt}}
\nonumber
\\&
+\sigma_t L^{\scaleto{l,m}{4pt}}
-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
= Q^{\scaleto{l,m}{4pt}}\quad .
\label{eq:rpn_m_=_z}
\end{align}
%and for $m>0$:
%\begin{align}
%&
%\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x L^{\scaleto{l-1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_x L^{\scaleto{l+1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m-1}{4pt}}\partial_x L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{l+1,-m+1}\partial_x L^{\scaleto{l+1,m-1}{4pt}}
%%\\&
%+\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_y L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_y L^{\scaleto{l+1,-m-1}{4pt}}
%%\nonumber
%%\\&
%+\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}e^{\scaleto{l-1,-m+1}{4pt}}%\partial_y L^{\scaleto{l-1,-m+1}{4pt}}
%\nonumber
%\\&
%-\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}f^{\scaleto{l+1,-m+1}{4pt}}%\partial_y L^{\scaleto{l+1,-m+1}{4pt}}
%%\\&
%+a^{\scaleto{l-1,-m}{4pt}}\partial_z L^{\scaleto{l-1,m}{4pt}}
%%\nonumber
%%\\&
%+b^{\scaleto{l+1,-m}{4pt}}\partial_z L^{\scaleto{l+1,m}{4pt}}
%\nonumber
%\\&
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%= Q^{\scaleto{l,m}{4pt}}
%%\nonumber
%\label{eq:rpn_m_>_z}
%\end{align}

For $m<0$ (upper sign) and $m>0$ (lower sign) we have
\begin{align}
&
\frac{1}{2}c^{\scaleto{l-1,\pm m-1}{4pt}}\partial_x L^{\scaleto{l-1,m\mp 1}{4pt}}
%\\&
-\frac{1}{2}d^{\scaleto{l+1,\pm m-1}{4pt}}\partial_x L^{\scaleto{l+1,m\mp 1}{4pt}}
%\\&
-\frac{1}{2}\beta_x^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m\pm 1}{4pt}}\partial_x L^{\scaleto{l-1,m\pm 1}{4pt}}
\nonumber
\\&
+\frac{1}{2}\beta_x^{\scaleto{m}{4pt}}f^{l+1,\pm m+1}\partial_x L^{\scaleto{l+1,m\pm 1}{4pt}}
%\\&
\mp \frac{1}{2}c^{\scaleto{l-1,\pm m-1}{4pt}}\partial_y L^{\scaleto{l-1,-m\pm 1}{4pt}}
\nonumber
\\&
\pm \frac{1}{2}d^{\scaleto{l+1,\pm m-1}{4pt}}\partial_y L^{\scaleto{l+1,-m \pm 1}{4pt}}
%\nonumber
%\\&
\mp \beta_y^{\scaleto{m}{4pt}}\frac{1}{2}e^{\scaleto{l-1,\pm m+1}{4pt}}\partial_y L^{\scaleto{l-1,-m\mp 1}{4pt}}
\nonumber
\\&
\pm \beta_y^{\scaleto{m}{4pt}}\frac{1}{2}f^{\scaleto{l+1,\pm m+1}{4pt}}\partial_y L^{\scaleto{l+1,-m\mp 1}{4pt}}
%\\&
+a^{\scaleto{l-1,\pm m}{4pt}}\partial_z L^{\scaleto{l-1,\mp m}{4pt}}
%\nonumber
%\\&
+b^{\scaleto{l+1,\pm m}{4pt}}\partial_z L^{\scaleto{l+1,\mp m}{4pt}}
\nonumber
\\&
+\sigma_t L^{\scaleto{l,m}{4pt}}
-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
= Q^{\scaleto{l,m}{4pt}}
\quad ,
%\nonumber
\label{eq:rpn_m_>_z}
\end{align}

with
\begin{align*}
\label{eq:real_sh_basis}
\beta_x^{m}=
\left\{
\begin{array}{ll}
0, & \text{for } m = -1\\
\frac{2}{\sqrt{2}}, & \text{for } m \neq 1\\
1, & \text{otherwise }
\end{array}
\right.
,\quad
\beta_y^{m}=
\left\{
\begin{array}{ll}
\frac{2}{\sqrt{2}}, & \text{for } m = -1\\
0, & \text{for } m \neq 1\\
1, & \text{otherwise }
\end{array}
\right.
\end{align*}

@@

%\vspace{1in}
\centering
\includegraphics[width=0.8\columnwidth]{fig_staggered_grids_small.pdf}
%\missingfigure{figures fig staggered grids}
%\vspace{-0.2in}
\icaption{\emph{Staggering} distributes the coefficients of the solution vector $\vec{u}$ onto four disjoint grids, indicated by the symbols, in a way which guarantees second order accuracy~\cite{Seibold14}.\vspace{-.2in}}
\label{fig:staggeredgrid}
\end{figure}

\begin{wrapfigure}{r}{0.6\columnwidth}
%\begin{center}
\hspace{-.1in}
\includegraphics[width=0.6\columnwidth]{fig_staggered_interpolation_small.pdf}
%\missingfigure{figures fig staggered interpolation}
\vspace{-.25in}
%\end{center}
\end{wrapfigure}Our solver supports placement of coefficients at arbitrary staggered grid locations (see Figure~\ref{fig:staggeredgrid}). This means that during the discretization step, the discrete location $(i, j, k)$ (at which the unknown is meant to be evaluated) might not coincide with the location of the unknown. To solve this, depending on how the two are located relative to each other, the parser returns an expression which interpolates the coefficients at $(i, j, k)$ from their defined locations. If those happen to coincide, the coefficient itself is returned. This is also done for RTE parameters, such as $\sigma_t$ or $p^{l,m}$, which are always located at the voxel center. We use the staggering scheme introduced by Seibold et al.~\cite{Seibold14} for their solver \textsf{StaRMAP}, which they proved ensures second order accuracy, i.e. a truncation error of $O(h^2)$, and prevents the growth of non-physical oscillations in the solution (see their paper for the full details of the staggered coefficient placement).

@@

%\subsection{System Building and Solving}
\tocless\subsection{Runtime}
\label{sec:solver_runtime}

@@

%-------------------------------------------------------------------------
\newpage
\tocless\section{Conclusion \label{sec:conclusion}}

@@

The real-valued $P_N$-equations are derived similar to their complex-valued counterpart, except that the real-valued SH basis functions $\SHBR$ are used instead of the complex-valued SH basis functions. The real-valued SH basis functions are defined in terms of complex-valued SH basis functions as follows:
% real valued SH ------------------
\begin{align}
\label{eq:real_sh_basis}
\SHBR^{l,m}=
\left\{
\begin{array}{lr}
\frac{\iu}{\sqrt{2}}\left(\SHBC^{l,m}-\left(-1\right)^m\SHBC^{l,-m}\right), & \text{for } m < 0\\
\SHBC^{l,m}, & \text{for } m = 0\\
\frac{1}{\sqrt{2}}\left(\SHBC^{l,-m}+\left(-1\right)^m\SHBC^{l,m}\right), & \text{for } m > 0
\end{array}
\right.
\end{align}
Note we use the subscript $\mathbb{R}$ and $\mathbb{C}$ do distinguish between real- and complex-valued SH basis functions respectively.

@@

\frac{1}{\sqrt{2}}c^{\scaleto{l-1,-1}{4pt}}\partial_y L^{\scaleto{l-1,-1}{4pt}}

@@

\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x

>>>>

Our method derives from the radiative transfer equation (RTE), which expresses the change of the radiance field $L$, with respect to an infinitesimal change of position in direction $\omega$ at point $\vec{x}$:
\begin{align}
%\label{eq:rte}
\left(\omega\cdot\nabla\right)L\left(\vec{x}, \omega \right)
=&
-\sigma_t\left(\vec{x}\right) L\left(\vec{x}, \omega \right)\nonumber\\
&
+\sigma_s\left(\vec{x}\right) \int_{\Omega}
{
p\left(\omega'\cdot\omega\right)L\left(\vec{x}, \omega' \right)\ud\omega'
}\nonumber\\
&
+Q\left(\vec{x}, \omega\right)\nonumber
\  .
\label{eq:rte}
\end{align}

@@

So far, we have only given the $P_N$-equations in high-level operator notation (Equation~\ref{eq:pn_operator_notation}). Carrying out the full derivation creates large, unwieldy equations and requires a string of expansions and applications of identities. These are challenging to manipulate if done by hand. We \rev{therefore used a computer algebra representation}, which allowed us to derive and discretize the $P_N$-equation in a semi-automatic fashion (Figure~\ref{fig:car}).

@@

Since the real-valued SH bases (Equation~\ref{eq:sh_real_basis}) have different definitions for $m<0$, $m=0$ or $m>0$,  we get different projections for $\mathcal{S}^{l,m}$, depending on the sign of $m$. Note that in cases where $L^{l,m}$ would appear with $l<0$ or $|m|>l$, this term is implicitly set to zero.
%\vspace{5in}
%\begin{align}
%&-\frac{1}{2}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m+1}{4pt}}
%%\\
%+\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m+1}{4pt}}
%%\\
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m-1}{4pt}}
%%\\
%+\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}e^{{l-1,m+1}}
%\partial_x
%L^{\scaleto{l-1,m+1}{4pt}}
%%\\
%+\frac{1}{2}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m+1}{4pt}}
%%\\
%-\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m-1}{4pt}}
%\nonumber
%\\&
%+a^{\scaleto{l-1,m}{4pt}}
%\partial_z
%L^{\scaleto{l-1,m}{4pt}}
%%\\
%+b^{\scaleto{l+1,m}{4pt}}
%\partial_z
%L^{\scaleto{l+1,m}{4pt}}
%%\\
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%%\\
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%%\\
%= Q^{\scaleto{l,m}{4pt}}
%\label{eq:rpn_m_<_z}
%\end{align}

For $m=0$ we have
\begin{eqnarray}
&&\frac{1}{\sqrt{2}} \left( 
         c^{\scaleto{l-1,-1}{4pt}} \partial_x L^{\scaleto{l-1,1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_x L^{\scaleto{l+1,1}{4pt}}  \right)
\nonumber \\
&& \frac{1}{\sqrt{2}} \left(
         c^{\scaleto{l-1,-1}{4pt}} \partial_y L^{\scaleto{l-1,-1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_y L^{\scaleto{l+1,-1}{4pt}}  \right)
\nonumber \\
&&+ \,a^{\scaleto{l-1,0}{4pt}} \partial_z L^{\scaleto{l-1,0}{4pt}}
  + \,b^{\scaleto{l+1,0}{4pt}} \partial_z L^{\scaleto{l+1,0}{4pt}} 
  +\,\sigma_t L^{\scaleto{l,m}{4pt}}
  -\,\sigma_s \lambda_{\scaleto{l}{4pt}} p^{\scaleto{l,0}{4pt}} L^{\scaleto{l,m}{4pt}}
 = Q^{\scaleto{l,m}{4pt}}\quad .
\label{eq:rpn_m_=_z}
\end{eqnarray}
%and for $m>0$:
%\begin{align}
%&
%\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x L^{\scaleto{l-1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_x L^{\scaleto{l+1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m-1}{4pt}}\partial_x L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{l+1,-m+1}\partial_x L^{\scaleto{l+1,m-1}{4pt}}
%%\\&
%+\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_y L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_y L^{\scaleto{l+1,-m-1}{4pt}}
%%\nonumber
%%\\&
%+\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}e^{\scaleto{l-1,-m+1}{4pt}}%\partial_y L^{\scaleto{l-1,-m+1}{4pt}}
%\nonumber
%\\&
%-\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}f^{\scaleto{l+1,-m+1}{4pt}}%\partial_y L^{\scaleto{l+1,-m+1}{4pt}}
%%\\&
%+a^{\scaleto{l-1,-m}{4pt}}\partial_z L^{\scaleto{l-1,m}{4pt}}
%%\nonumber
%%\\&
%+b^{\scaleto{l+1,-m}{4pt}}\partial_z L^{\scaleto{l+1,m}{4pt}}
%\nonumber
%\\&
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%= Q^{\scaleto{l,m}{4pt}}
%%\nonumber
%\label{eq:rpn_m_>_z}
%\end{align}

For $m<0$ (upper sign) and $m>0$ (lower sign) we have
\begin{align}
  \frac{1}{2} c^{\scaleto{l-1,\pm m-1}{4pt}} \partial_x L^{\scaleto{l-1,m\mp 1}{4pt}}
&-\frac{1}{2} d^{\scaleto{l+1,\pm m-1}{4pt}} \partial_x L^{\scaleto{l+1,m\mp 1}{4pt}}
\nonumber \\
 -\frac{1}{2} \beta_x^{\scaleto{m}{4pt}} e^{\scaleto{l-1, m\pm 1}{4pt}} \partial_x L^{\scaleto{l-1,m\pm 1}{4pt}}
&+\frac{1}{2} \beta_x^{\scaleto{m}{4pt}} f^{\scaleto{l+1,\pm m+1}{4pt}} \partial_x L^{\scaleto{l+1,m\pm 1}{4pt}}
\nonumber \\
 \mp \frac{1}{2} c^{\scaleto{l-1,\pm m-1}{4pt}} \partial_y L^{\scaleto{l-1,-m\pm 1}{4pt}}
&\pm \frac{1}{2} d^{\scaleto{l+1,\pm m-1}{4pt}} \partial_y L^{\scaleto{l+1,-m \pm 1}{4pt}}
\nonumber \\
 \mp \frac{1}{2} \beta_y^{\scaleto{m}{4pt}} e^{\scaleto{l-1,\pm m+1}{4pt}} \partial_y L^{\scaleto{l-1,-m\mp 1}{4pt}}
&\pm \frac{1}{2} \beta_y^{\scaleto{m}{4pt}} f^{\scaleto{l+1,\pm m+1}{4pt}} \partial_y L^{\scaleto{l+1,-m\mp 1}{4pt}}
\nonumber \\
+a^{\scaleto{l-1,\pm m}{4pt}}\partial_z L^{\scaleto{l-1,\mp m}{4pt}}
+b^{\scaleto{l+1,\pm m}{4pt}}\partial_z L^{\scaleto{l+1,\mp m}{4pt}}
&+\sigma_t L^{\scaleto{l,m}{4pt}}
-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
= Q^{\scaleto{l,m}{4pt}}  \;
\label{eq:rpn_m_>_z}
\end{align}
with
\begin{align*}
\label{eq:real_sh_basis}
\beta_x^{m}=
\left\{
\begin{array}{ll}
0, & \text{for } m = -1\\
\frac{2}{\sqrt{2}}, & \text{for } m \neq 1\\
1, & \text{otherwise }
\end{array}
\right.
,\quad
\beta_y^{m}=
\left\{
\begin{array}{ll}
\frac{2}{\sqrt{2}}, & \text{for } m = -1\\
0, & \text{for } m \neq 1\\
1, & \text{otherwise }
\end{array}
\right.
\end{align*}

@@

%\vspace{1in}
\centering
\includegraphics[width=0.8\columnwidth]{fig_staggered_grids_small.pdf}
%\missingfigure{figures fig staggered grids}
%\vspace{-0.2in}
\icaption{\emph{Staggering} distributes the coefficients of the solution vector $\vec{u}$ onto disjoint grids, indicated by the symbols, in a way which guarantees second order accuracy~\cite{Seibold14}.\vspace{-.2in}}
\label{fig:staggeredgrid}
\end{figure}

\begin{wrapfigure}{r}{0.5\columnwidth}
%\begin{center}
\hspace{-.1in}
\includegraphics[width=0.5\columnwidth]{fig_staggered_interpolation_small.pdf}
%\missingfigure{figures fig staggered interpolation}
\vspace{-.25in}
%\end{center}
\end{wrapfigure}Our solver supports placement of coefficients at arbitrary staggered grid locations (see Figure~\ref{fig:staggeredgrid}). This means that during the discretization step, the discrete location $(i, j, k)$ (at which the unknown is meant to be evaluated) might not coincide with the location of the unknown. To solve this, depending on how the two are located relative to each other, the parser returns an expression which interpolates the coefficients at $(i, j, k)$ from their defined locations. If those happen to coincide, the coefficient itself is returned. This is also done for RTE parameters, such as $\sigma_t$ or $p^{l,m}$, which are always located at the voxel center. We use the staggering scheme introduced by Seibold et al.~\cite{Seibold14} for their solver \textsf{StaRMAP}, which they proved ensures second order accuracy, i.e. a truncation error of $O(h^2)$, and prevents the growth of non-physical oscillations in the solution. This involves placing the SH coefficients onto disjoint grids --- 4 in 2D as in Figure~\ref{fig:staggeredgrid}, and 8 in 3D (see their paper for the full details of the staggered coefficient placement).
\vspace{-.15in}

@@

%\subsection{System Building and Solving}
\tocless\subsection{Runtime \label{sec:solver_runtime}}

@@

\newpage
\tocless\section{Conclusion \label{sec:conclusion}}

@@

The real-valued $P_N$-equations are derived similar to their complex-valued counterpart, except that the real-valued SH basis functions $\SHBR$ are used instead of the complex-valued SH basis functions. The real-valued SH basis functions are defined in terms of complex-valued SH basis functions as follows:
% real valued SH ------------------
\begin{align}
\label{eq:real_sh_basis}
\SHBR^{l,m}=
\left\{
\begin{array}{lr}
\frac{\iu}{\sqrt{2}}\left(\SHBC^{l,m}-\left(-1\right)^m\SHBC^{l,-m}\right), & \text{for } m < 0\\
\SHBC^{l,m}, & \text{for } m = 0\\
\frac{1}{\sqrt{2}}\left(\SHBC^{l,-m}+\left(-1\right)^m\SHBC^{l,m}\right), & \text{for } m > 0
\end{array}
\right.
\end{align}
Note we use the subscript $\mathbb{R}$ and $\mathbb{C}$ to distinguish between real- and complex-valued SH basis functions respectively.

@@

+\frac{1}{\sqrt{2}}c^{\scaleto{l-1,-1}{4pt}}\partial_y L^{\scaleto{l-1,-1}{4pt}}

@@

\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x L^{\scaleto{l-1,-m-1}{4pt}}
